Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-05 tex/results.tex
fix word choice
mention in caption ata from Rockstuhl is scattering

It is worth noting that the extinction cross-section curve in Figure \ref{fig:cube535} has extra peaks 
compared to the results of Figure 18 of Rockstuhl et al., due to the three-dimensional effects captured in our simulation and the sharp 
edges, the latter effect also being mentioned by Rockstuhl et al. The 3D effects will be approached
in the following results, where we attempt a replication of one of the results on Figure 14 of Rockstuhl et al.

@@

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by hand using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main resonance peaks presented in Rockstuhl et al.\ are 
closely matched. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
    \caption{Replication of the results in Figure 14 of Rockstuhl et al., 2005. Extinction cross-section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the $z$-axis.}
    \label{fig:rep_14}
 \end{figure}

>>>>

It is worth noting that the extinction cross-section curve in Figure \ref{fig:cube535} has extra peaks 
compared to the results of Figure 18 of Rockstuhl et al., due to the three-dimensional effects captured in our simulation and the sharp 
edges, the latter effect also being mentioned by Rockstuhl et al. The 3D effects will be addressed
in the following results, where we attempt a replication of one of the results on Figure 14 of Rockstuhl et al.

@@

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by hand using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main resonance peaks presented in Rockstuhl et al.\ are 
closely matched. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry, 
as well as the fact that we compute extinction cross-section, while Rockstuhl et al.\ report scattering.

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
    \caption{Replication of the results in Figure 14 of Rockstuhl et al., 2005. Extinction cross-section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the $z$-axis (green line). 
    The digitized curve from Rockstuhl et al.\ corresponds to scattering (orange line).}
    \label{fig:rep_14}
 \end{figure}
